---
title: "Introduction to the sunBcubed package"
author: "Sandra MacFadyen"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to the sunBcubed package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(sunBcubed)
```

## Mathematical Biosciences Lab
Our lab is a multidisciplinary research team at the interface of mathematics and biology/life sciences. As part of the Department of Mathematical Sciences at Stellenbosch University in South Africa, we are a dynamic research group led by Prof Cang Hui, a SARChI Chair in Mathematical and Theoretical Physical Biosciences. Our interests lie in proposing models and theories for explaining emerging patterns in ecology. Ecology studies biodiversity in its variety and complexity. As ecological processes are highly complex and adaptive, we rely on the simplicity of mathematical language to build models and theoretical frameworks.

## B-Cubed toolbox for biodiversity monitoring  
B-Cubed is tackling the urgent challenge of understanding the global biodiversity crisis by offering fast, reliable, and consistent data that policy makers can use to make informed decisions. We bridge the gap between various data sources—ranging from citizen scientists and museums to research institutions—to create a more comprehensive view of biodiversity. Our approach uses data cubes and the Essential Biodiversity Variables framework to standardize this information, making it easier to monitor changes in biodiversity over time. SUN and other project teams work hand-in-hand with existing biodiversity programs to pinpoint policy needs and improve data integration. Our real-time, cloud-based models provide valuable insights into past, present, and future biodiversity trends. To encourage further research and application, we're developing automated workflows for data modeling and change indicators. B-Cubed's effectiveness is showcased in four diverse case studies, each varying in geographic scale, biodiversity richness, and data availability.

## Deliverables
SUN deliverables for EU Horizon B3 project: Biodiversity Building Blocks for Policy ([https://b-cubed.eu/](https://b-cubed.eu/))

#### SUN is leading the follwing tasks
```
Task 4.2: Dissimilarity cube
Task 4.3: Network invasibility cube
Task 5.3: Indicators on impacts of alien taxa
```

#### SUN is a partner on the following tasks
```
Task 1.6: International Science-Policy convergence [JLUG] 
Task 1.8: Sustainability [APM] 
Task 2.1: Species occurrence cube specification [INBO] 
Task 3.1: Software requirements and quality assessment [INBO] 
Task 3.2: Documentation and tutorials [APM] 
Task 4.1: Suitability cube [APM] 
Task 5.1: General biodiversity variables and indicators [JLUG] 
Task 5.4: Quantify indicator robustness [INBO] 
Task 5.5: Integration of functions into an R package [INBO] 
Task 6.2: Case study 2 - Biological invasions in South Africa [SANBI]
```


## Funding
B-Cubed (Biodiversity Building Blocks for policy) receives funding from the European Union’s Horizon Europe Research and Innovation Programme  (ID No 101059592). Views and opinions expressed are however those of the author(s) only and do not necessarily reflect those of the European Union or the European Commission. Neither the EU nor the EC can be held responsible for them.
