---
title: "Introduction to using `simData()`"
author: "Sandra MacFadyen"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to using `simData()`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
if (requireNamespace("terra", quietly = TRUE) && requireNamespace("ggplot2", quietly = TRUE)) {
  library(terra)
  library(ggplot2)
  library(dplyr)
  } else {
    stop("The packages 'terra', 'ggplot2' and 'dplyr' are required for this example.")
  }

library(sunBcubed)
```

#### Overview
This vignette provides an introduction to the `simData()` function from the `sunBcubed` package. The function is designed to simulate ecological data across a spatial and temporal grid, which can be used for testing spatial analysis methods or for educational purposes.

#### Simulating Data
We will start by simulating a basic dataset with default parameters.

```{r}
# Set seed for reproducibility
set.seed(123)

# Simulate data
sim_data = simData(returnOption = 1, plot = FALSE)
head(sim_data)
```

#### Visualizing Data
If you want to visualize the spatial distribution of species counts, you can set the plot parameter to `TRUE`. Here we demonstrate this with `returnOption = 1`, which outputs a summary table of species by site and plots the data.

```{r plot-example, fig.width=7, fig.height=4}
# Generate data and plot
site_species = simData(returnOption = 1, plot = TRUE)
head(site_species)
```

#### Advanced Usage
The `simData()` function can also return a `SpatRaster` object or a distance matrix. Here's how to use these options:

```{r}
# Generate a SpatRaster object
raster_data = simData(returnOption = 2, plot = FALSE)
raster_data

# Calculate and return a distance matrix
distance_matrix = simData(returnOption = 3, plot = FALSE)
head(distance_matrix)
```

#### Saving Data to the Global Environment
If you need to access the raw grid data for further analysis, you can save it to the global environment using the globalSave option.

```{r}
site_species = simData(returnOption = 1, plot = FALSE, globalSave = TRUE)
# head(site_species)

# Accessing the grid data from global environment
head(simData_grid)
```

#### Conclusion
This vignette has introduced the basic functionalities of the `simData()` function. For more detailed information, please refer to the package documentation.
