---
title: "Introduction to using `denGEN()`"
author: "Sandra MacFadyen"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to using `denGEN()`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
if (requireNamespace("terra", quietly = TRUE) && requireNamespace("ggplot2", quietly = TRUE)) {
  library(terra)
  library(ggplot2)
  library(dplyr)
  } else {
    stop("The packages 'terra', 'ggplot2' and 'dplyr' are required for this example.")
  }

library(sunBcubed)
```

This is an introduction to using the `dataGEN` function developed by Stellenbosch BioMath for the b-cubed project.

The function prepares data from other cubes and accessible datasets as follows:

1. Prepare data from other cubes and accessible datasets
2. Include details for spatial extent e.g. spatial polygons, shapefiles, squares (corner coordinates)
3. Include details for spatial resolution, specified and default
4. Ensure alien status of identified species is listed (we need to make a decision on species list completeness, considering other cubes and SDM cubes, etc.)
5. Include details for temporal range
6. Allow for different options e.g. option = 1, 2; 1 for `dissim()` and 2 for `invasib()`
7. Return, site by species, site by xyt, site by env, site by site distance; species by trait, species by species phylogenetic distance, matrices (and default setting if null)
