---
title: "Introduction to using `dissim()`"
author: "Sandra MacFadyen"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to using `dissim()`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
if (requireNamespace("terra", quietly = TRUE) && requireNamespace("ggplot2", quietly = TRUE)) {
  library(terra)
  library(ggplot2)
  library(dplyr)
  } else {
    stop("The packages 'terra', 'ggplot2' and 'dplyr' are required for this example.")
  }

library(sunBcubed)
```

This is an introduction to using the `dissim` function developed by Stellenbosch BioMath for the b-cubed project.

The `dissim()` function creates the dissimialrity cube as follows:

1. Takes data created using the `dataGEN()` function
2. `dataGEN` option 1 returns metrics of spatial and temporal turnovers. There needs to be practical solution to visualise higher-order zeta (order 1 richness [related Hill numbers], order 2 beta with different metrics)
3. Return, visualisation options [maps GeoTIFFs], site by site matrices, per temporal unit. Temporal hotspots, statistics tables, PCA/NMDS and CCA visualisation.
4. Include functional/phylogenetic dissimilarity?
5. Send outputs to Zenodo
