---
title: "Introduction to using `invasib()`"
author: "Sandra MacFadyen"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to using `invasib()`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
if (requireNamespace("terra", quietly = TRUE) && requireNamespace("ggplot2", quietly = TRUE)) {
  library(terra)
  library(ggplot2)
  library(dplyr)
  } else {
    stop("The packages 'terra', 'ggplot2' and 'dplyr' are required for this example.")
  }

library(sunBcubed)
```

This is an introduction to using the `invasib` function developed by Stellenbosch BioMath for the b-cubed project.

The `invasib()` function creates the invasibility cube as follows:

1. Takes data created using the `dataGEN()` function
2. Calculates trait distance matrix
3. Allow user to specify SD of interaction kernel (could be assessed based on trait distance histogram or from 0 to max distance)
4. Allow user to specify trait axes (could be PCA axes), incl. phylo?
5. Community trait profile, invasibility figure, trait specific invasiveness(function)
6. Return, invasive(trait) function, visual
7. Send outputs to Zenodo
